% ============================================================
% Divit Mittal — Curriculum Vitae
% Engine: pdflatex / xelatex
% Class:  moderncv (classic, blue)
% ============================================================
\documentclass[11pt,a4paper]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[top=1.8cm, bottom=1.8cm, left=2cm, right=2cm]{geometry}
\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage{xcolor}

% Tighten bullet list spacing inside \cventry descriptions
\setlist[itemize]{topsep=2pt, itemsep=1pt, parsep=0pt, leftmargin=1.4em}

% ── Personal data ────────────────────────────────────────────
\name{Divit}{Mittal}
\phone[mobile]{+91~9718898585}
\email{divitmittal@outlook.in}
\homepage{divit.site}
\social[github]{DivitMittal}
\social[linkedin]{divit-mittal}
\extrainfo{%
  \faRobot~\href{https://huggingface.co/divitmittal}{huggingface.co/divitmittal}
  \quad
  \faChartBar~\href{https://www.kaggle.com/divitmittal}{kaggle.com/divitmittal}%
}

% ============================================================
\begin{document}
\makecvtitle
\vspace{-1.5em}

% ── Professional Summary ─────────────────────────────────────
\section{Professional Summary}
\cvitem{}{%
  Infrastructure engineer and functional programming specialist with deep expertise in
  Nix/NixOS, AI/ML, and cloud data engineering. Delivered production consulting work for
  Tweag (Blockfrost, ModusCreate) optimising CI/CD pipelines and package derivations.
  Conducted funded research in computer vision transformers at Manipal University.
  Expert in declarative infrastructure, reproducible builds, and type-safe system design
  across Linux/macOS/Android platforms.%
}

% ── Skills ───────────────────────────────────────────────────
\section{Skills}

\cvitem{\textbf{ML \& Data Science}}{%
  Deep Learning: Keras \& PyTorch /
  Machine Learning: scikit-learn, TensorFlow /
  LLM: Transformers, RAG, Encoders \& Decoders /
  Big Data: Hadoop, Spark, Hive, Kafka /
  Dashboarding: MS PowerBI /
  Image (DL): Vision Transformers, Semantic Segmentation, GANs, Siamese /
  Computer Vision: OpenCV, ITK /
  MLOps: HuggingFace, Gradio, Kaggle%
}

\cvitem{\textbf{DevOps \& SysAdmin}}{%
  NixOS Expert /
  IaC: Nix, Ansible \& Terraform /
  Shells: Bash, Zsh, Fish, Pwsh /
  CI/CD: GitHub Actions \& Hydra /
  Cloud: AWS (Lambda, S3, Glue, SageMaker, API Gateway) /
  Declarative Agentic AI Workflows /
  VCS: Git \& Jujutsu /
  Virtualisation \& Containerisation: Proxmox, KVM, Docker \& Podman%
}

\cvitem{\textbf{Functional Programming}}{%
  Haskell: FFI, Cabal, type-safe DSL design, monad transformers /
  Nix Expression Language: advanced derivations, flakes, overlays, cross-compilation /
  Web: Svelte, TypeScript /
  Systems: C/C++ interop, LLVM /
  Audio DSP: Faust, signal processing%
}

% ── Work Experience ───────────────────────────────────────────
\section{Work Experience}

\cventry{07/2024--Present}{Nix Ecosystem Consultant}{Tweag}{Remote}{Paid Consulting}{%
  Advanced Nix ecosystem consulting across enterprise client projects.
  \begin{itemize}
    \item \textbf{Blockfrost Cardano Node Integration:} Architected Nix package derivations
      for Blockfrost's Cardano blockchain infrastructure; achieved reproducible deployments
      eliminating dependency conflicts and build failures.
      \textit{Stack: Nix, Cardano Node, Blockfrost API, Haskell ecosystem}
    \item \textbf{ModusCreate CI/CD Automation:} Designed declarative CI/CD pipelines using
      NixOS and Hydra; reduced build times via binary caching, achieved 100\% reproducible
      deployments, eliminated ``works on my machine'' issues.
      \textit{Stack: NixOS, Hydra, CI/CD, IaC}
    \item Additional: enterprise configuration management, complex dependency resolution,
      cross-platform builds, infrastructure cost optimisation via caching.
  \end{itemize}%
}

\cventry{12/2021--02/2022}{DevOps \& System Administrator}{UbiOps (Yes!Delft)}{Delft, Netherlands}{}{%
  Administered containerised environments using Docker/Kubernetes for multi-tenant ML
  workloads, implemented CI/CD pipelines for automated model deployment, and maintained
  cloud infrastructure across AWS/GCP.%
}

% ── Research Experience ───────────────────────────────────────
\section{Research Experience}

\cventry{05/2025--08/2025}{Funded Deep-Learning Research Position}{Manipal University Jaipur}{Jaipur, India}{Dept.\ of Applied Statistics \& Data Science}{%
  Research on hybrid transformer (FocalViT + CrossViT) for multi-focus image fusion (MFIF).
  \begin{itemize}
    \item \textbf{Architecture:} Combines FocalViT's hierarchical focal attention with
      CrossViT's cross-branch interaction for superior spatial-spectral feature extraction.
    \item \textbf{Results:} State-of-the-art fusion quality on benchmark datasets;
      improved high-frequency detail preservation over CNN-based approaches.
    \item \textbf{Deployment:} PyTorch model on HuggingFace Model Hub + Spaces and Kaggle.
    \item \textit{Stack: PyTorch, Transformers, Computer Vision, Gradio, HuggingFace}
    \item \href{https://huggingface.co/spaces/divitmittal/HybridTransformer-MFIF}{Demo}
      \textbar{} \href{https://github.com/DivitMittal/HybridTransformer-MFIF}{Code}
      \textbar{} \href{https://kaggle.com/datasets/divitmittal/lytro-multi-focal-images}{Dataset}
  \end{itemize}%
}

% ── Projects ─────────────────────────────────────────────────
\section{Projects}

\cventry{08/2024--10/2024}%
  {hs-faust: Haskell DSL for Faust Audio Signal Processing}%
  {\href{https://github.com/DivitMittal/hs-faust}{github.com/DivitMittal/hs-faust}}{}{}%
{%
  GSoC 2025 proposal project developed with Faust project maintainers.
  \begin{itemize}
    \item Type-safe Haskell bindings over Faust's C Signal API; compile-time prevention
      of DSP errors (feedback loops, sample rate mismatches).
    \item Interfaces with Faust compiler to generate LLVM IR and C++ from Haskell-defined
      signal graphs.
    \item \textit{Stack: Haskell, FFI, Faust, C/C++ interop, LLVM, Nix}
  \end{itemize}%
}

\cventry{04/2024--Present}%
  {OS-nixCfg: State-of-the-Art Infrastructure as Code Configuration \normalfont{(17~\faStar)}}%
  {\href{https://github.com/DivitMittal/OS-nixCfg}{github.com/DivitMittal/OS-nixCfg}}{}{}%
{%
  \begin{itemize}
    \item Unified declarative configuration for 4+ platforms (macOS/nix-darwin,
      NixOS, Android/nix-on-droid, WSL2); complete deterministic reproducibility.
    \item Starred by DRW employees; implements flake-parts, agenix/ragenix secrets
      management, nix-topology network visualisation, GitHub Actions CI/CD.
    \item 100+ custom Home Manager modules, package derivations, overlays.
    \item \textit{Stack: Nix, nix-darwin, NixOS, home-manager, flake-parts, agenix}
  \end{itemize}%
}

\cventry{09/2024--Present}%
  {TLTR: Cross-Platform Multi-Layer Keyboard Layout \normalfont{(11~\faStar)}}%
  {\href{https://github.com/DivitMittal/TLTR}{github.com/DivitMittal/TLTR}}{}{}%
{%
  \begin{itemize}
    \item 38-key, 4-layer Colemak Mod-DH layout for programmer ergonomics; deployed via
      Kanata (cross-platform), Karabiner-Elements (macOS), and QMK firmware on
      RP2040-based Piantor split keyboard.
    \item \textit{Stack: QMK (C), Kanata, Karabiner-Elements, Nix Flakes, keymap-drawer}
  \end{itemize}%
}

\cventry{06/2025--Present}%
  {hammerspoon-nix: Declarative macOS Automation via Nix \normalfont{(10~\faStar)}}%
  {\href{https://github.com/DivitMittal/hammerspoon-nix}{github.com/DivitMittal/hammerspoon-nix}}{}{}%
{%
  \begin{itemize}
    \item First-class \texttt{programs.hammerspoon} Home Manager option supporting
      package management, \texttt{configPath}, and declarative Spoon installation.
    \item \textit{Stack: Nix, Lua, Hammerspoon, macOS, home-manager, flake-parts}
  \end{itemize}%
}

\cventry{06/2025--Present}%
  {firefox-nixCfg: Declarative Firefox Configuration via Nix \normalfont{(14~\faStar)}}%
  {\href{https://github.com/DivitMittal/firefox-nixCfg}{github.com/DivitMittal/firefox-nixCfg}}{}{}%
{%
  \begin{itemize}
    \item All Firefox preferences, extensions, and userChrome/userContent CSS managed as
      Nix code; integrates BetterFox hardened profile, Tridactyl, and Sideberry.
    \item \textit{Stack: Nix, JavaScript (autoconfig), CSS (userChrome), home-manager}
  \end{itemize}%
}

\cventry{02/2024}%
  {DocAssist-LLM @ IEEE MUJ}%
  {\href{https://github.com/DivitMittal/DocAssist-LLM}{github.com/DivitMittal/DocAssist-LLM}}{}{}%
{%
  \begin{itemize}
    \item RAG-enhanced LLaMA-like transformer for programming documentation assistance,
      built entirely from scratch (tokenisation \textrightarrow{} embeddings \textrightarrow{} output probabilities).
    \item RAG via Qdrant vector database on DigitalOcean Docker; Streamlit front-end.
    \item \textit{Stack: Python, Transformers, RAG, Qdrant, Docker, Streamlit, DigitalOcean}
  \end{itemize}%
}

\cventry{10/2023}%
  {Hazard Map for Lunar Lander Navigation @ SIH}{}{}{}%
{%
  \begin{itemize}
    \item Hazard detection using ISRO Chandrayaan-2 TMC2 \& OHRC sensor data;
      fused multispectral high-res imagery and stereo-triplet panchromatic data.
    \item Applied SRGANs, DCNNs, and semantic segmentation for safe landing site
      identification.
    \item \textit{Stack: Python, TensorFlow, SRGANs, DCNNs, Computer Vision, Satellite Imagery}
  \end{itemize}%
}

\cventry{04/2025}%
  {Blinkit Customer Churn Analysis}%
  {\href{https://github.com/DivitMittal/Blinkit-Churn-Analysis}{github.com/DivitMittal/Blinkit-Churn-Analysis}}{}{}%
{%
  \begin{itemize}
    \item H2O.ai AutoML for churn prediction; interactive PowerBI dashboards for
      stakeholder exploration; Sweetviz for automated data profiling.
    \item \textit{Stack: Python, H2O.ai AutoML, PowerBI, Sweetviz}
  \end{itemize}%
}

% ── Hackathons & Competitions ─────────────────────────────────
\section{Hackathons \& Competitions}

\cventry{09/2024}{BobbleAI Datathon Winner}{BobbleAI Keyboard}{Gurgaon, Haryana, India}{}{%
  Processed 8 million event records (70M+ user base) from BobbleAI Keyboard over 5 days.
  Extracted \& transformed JSON; ML-filtered and stored as Apache Parquet on AWS S3 via
  serverless AWS Lambda and PySpark on AWS Glue.
  \textit{Stack: AWS Lambda, AWS Glue, PySpark, AWS S3, Apache Parquet, Python}
  \quad \href{https://github.com/DivitMittal/Datathon-BigData}{github.com/DivitMittal/Datathon-BigData}%
}

\cventry{10/2023}{Proglint's Computer Vision 2k23 National Hackathon Winner}{Alliance University}{Anekal, Karnataka, India}{}{%
  \begin{itemize}
    \item \textbf{CARLA Autonomous Driving:} High-fidelity CARLA simulator with RGBA \&
      LiDAR sensors; CNNs for semantic segmentation.
      \href{https://github.com/DivitMittal/CARLA-Autonomous-Driving}{Code}
    \item \textbf{Driver Drowsiness Detection:} Siamese Neural Networks + Haar cascade
      wave filters for real-time facial fatigue detection.
      \href{https://github.com/DivitMittal/Driver-Drowsiness-Detection}{Code}
  \end{itemize}%
}

% ── Honours & Awards ──────────────────────────────────────────
\section{Honours \& Awards}

\cvitem{01/2020}{\textbf{International Rank 7} --- International Mathematics Olympiad (IMO), The Science Olympiad Foundation, New Delhi}

\cvitem{12/2019}{\textbf{International Rank 49} --- International English Olympiad (IEO), The British Council Division / British High Commission, New Delhi}

\cvitem{01/2019}{\textbf{India National Level Runner-up} --- Vidyarthi Vigyan Manthan, Vijnana Bharati (VIBHA) with Vigyan Prasar, under DST \& NCERT}

% ── Education ─────────────────────────────────────────────────
\section{Education \& Training}

\cventry{09/2022--Present}%
  {B.Tech in Data Science \& Engineering}%
  {Manipal University Jaipur}{Jaipur, Rajasthan, India}%
  {CGPA: 8.0/10 \textbar{} NQF: NCC5}{}

\cventry{09/2021--09/2022}%
  {B.Sc in Computer Science \& Engineering}%
  {Delft University of Technology}{Delft, Netherlands}%
  {Grade: 8.0/10 \textbar{} 20 ECTS}%
  {\href{https://europa.eu/!yp79Jh}{Diploma} \textbar{} \href{https://europa.eu/!BB98Ww}{Transcript}}

\cventry{08/2020}%
  {B.Computing in Computer Science (Summer School)}%
  {National University of Singapore}{Singapore}{}{}

\cventry{03/2018--07/2020}%
  {All India Senior School Certificate Examination (Class XII)}%
  {CBSE --- Delhi Public School, R.K. Puram}{New Delhi, India}%
  {A1~$\approx$96\% \textbar{} NSQF Level 4 (NCC 2)}%
  {\href{https://europa.eu/!yp79Jh}{Diploma} \textbar{} \href{https://europa.eu/!BB98Ww}{Transcript}}

\cventry{03/2016--05/2018}%
  {All India Secondary School Examination (Class X)}%
  {CBSE --- Bhatnagar International School, Bhera Enclave}{New Delhi, India}%
  {A1~$\approx$97\% \textbar{} NSQF Level 2 (NCWP 2)}%
  {\href{https://europa.eu/!Mv98jr}{Diploma} \textbar{} \href{https://europa.eu/!uG83GN}{Transcript}}

% ── Language Skills ───────────────────────────────────────────
\section{Language Skills}

\cvitem{Mother tongue}{Hindi}

\cvitem{German}{%
  Goethe-Zertifikat B2 ---
  Listening: B2 \textbar{} Reading: B2 \textbar{} Writing: B2 \textbar{}
  Spoken Production: B2 \textbar{} Spoken Interaction: B2%
}

\cvitem{English}{%
  IELTS ---
  Listening: C2 \textbar{} Reading: C2 \textbar{} Writing: C1 \textbar{}
  Spoken Production: C1 \textbar{} Spoken Interaction: C2%
}

\end{document}
